---
title: Automated classification of movement types based on GPS-dervived features
subtitle: leveraging GPS data to classify different types of active movements hiking, jogging, ski touring and cycling.
author: Johannes Guler and Michael Fehr
format:
  html:
    code-fold: true
execute:
  warning: false
  message: false
lang: en  
bibliography: bibliography.bib
---

```{r preprocessing}
#| code-summary: preprocessing

``` 
#test rendering MF

## Abstract

This project aims to identify different types of active movement based on personal GPS data. By integrating additional data from Swiss TLM3D, which includes detailed information on street networks and hiking paths, we aim to accurately classify movement types based on GPS-derived features such as speed, elevation change, distance measures, and month of activity. The classification is performed using a decision tree model in R Studio. The effectiveness of this approach is evaluated using predictive validation metrics including accuracy, precision, recall, and F1-score. The validation is performed using personal GPS data such as hiking, jogging, ski-touring, and cycling that were collected via the Strava app over a period of 3 months. 

## Introduction

### Background



## Material and Methods

## Results

## Discussion

## Appendix

### Wordcount

<!-- after installing the wordcountadding, remove the line "#| eval: false" -->

```{r wordcount}
# install.packages("pacman") 
library("pacman")

p_install_gh("benmarwick/wordcountaddin")

wordcountaddin::word_count("index.qmd")
```


